---
title: "Assignment 3: Regular Expressions and String Functions"
author: "Katherine Evers"
date: "2/16/2019"
output: html_document
---
### 3. Copy the introductory example. The vector "name" stores the extracted names.

```{r}
raw.data <- "555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"

library(stringr)

name <-  unlist(str_extract_all(raw.data, "[[:alpha:]., ]{2,}"))
name
```

**(a) Use the tools of this chapter to rearrange the vector so that all elements conform to the standard first_name last_name.**

Extract first names:
```{r}
#from first name last name format:
firstName <- unlist(str_extract_all(name, "[[:alpha:]]{2,} "))
firstName
```


```{r}
#from last name, first name format
first <- unlist(str_extract_all(name, ", [[:alpha:].+]{1,}+"))
first
```


```{r}
#extract name without comma and space
FirstName <- sub(".*? (.+)", "\\1", first)
FirstName
```


```{r}
firstNames <- c(firstName, FirstName)
firstNames
```

Extract last names:
```{r}
#from first name last name format:
lastName <- unlist(str_extract_all(name, "\\b .+\\b"))
lastName
```

```{r}
#extract name without space before
lastName1 <- sub(".*? ", "\\1", lastName)
lastName1
```

```{r}
#from last name, first name format
last <- unlist(str_extract_all(name, "[[:alpha:]]{2,},"))
last
```

```{r}
#extract name without comma
LastName <- sub(",", "\\1", last)
LastName
```

```{r}
lastNames <- c(lastName1, LastName)
lastNames
```

Create a data frame with first names and last names:
```{r}
df <- data.frame("First Name" = firstNames, "Last Name" = lastNames)
knitr::kable(df)

```

Create a vector of first and last names:
```{r}
namesVector <- paste0(firstNames,' ',lastNames)
namesVector
```


**(b) Construct a logical vector indicating whether a character has a title (i.e., Rev. and Dr.).**
    
```{r}
prefix <- (str_extract_all(name, "[[A-z]]{2,}\\."))
prefix

title <- str_detect(name, "[[:alpha:]]{2,}\\.")
title
```


**(c) Construct a logical vector indicating whether a character has a second name.**

```{r}
middleName <- str_extract_all(name,"\\,\\s\\w\\.\\s[[:alpha:]]{2,}")
middleName

secondName <- str_detect(name,"\\,\\s\\w\\.\\s[[:alpha:]]{2,}")
secondName
```
### 4. Describe the types of strings that conform to the following regular expressions and construct an example that is matched by the regular expression.**

    **(a) [0-9]+\\$**
        This expression returns strings of 1 or more numbers followed by a $.
```{r}
example1 <- "35iu68903$64678$t8bhj$246"
str_extract_all(example1, "[0-9]+\\$" )
```
        
    **(b) \\b[a-z]{1,4}\\b**
        This expression returns strings of 1-4 lowercase letters
```{r}
example2 <- c("abc", "de", "f", "ghij", "kl123")
str_extract_all(example2, "\\b[a-z]{1,4}\\b")
```
  
    **(c) .*?\\.txt$**
        This expression returns strings that end with ".txt"
```{r}
example3 <- c("abc.txt", "abc.doc", "txt")
str_extract_all(example3, ".*?\\.txt$")
```
        
    
    **(d) \\d{2}/\\d{2}/\\d{4}**
        This string returns date formats: any 2 digits, forward slash, any 2 digits, forward slash, any 4 digits
        
```{r}
example3 <- c("02/11/2019", "2/11/19", "04/02/2018", "1789/12", "12387689")
str_extract_all(example3, "\\d{2}/\\d{2}/\\d{4}")
```
        
    
    **(e) <(.+?)>.+?</\\1>**
        This expression returns strings that have html format
```{r}
example4 <- c("<p>Hello world</p>", "Hello", "<Hi>")
str_extract_all(example4,"<(.+?)>.+?</\\1>")
```
        

### 9. The following code hides a secret message. Crack it with R and regular expressions. Hint: Some of the characters are more revealing than others! The code snippet is also available in the materials at www.r-datacollection.com.**

    clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr
    
```{r}
message <- "clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr"

#Remove numbers
message <- unlist(str_extract_all(message, "[^[:digit:]]"))
message

#Remove lower case letters
message1 <- unlist(str_extract_all(message, "[^[:lower:]]"))
message1

#Concatenate individual letters
message2 <- paste(message1, collapse = '')
message2

#Replace periods with spaces
message3 <- unlist(str_replace_all(message2,"\\.", " "))
message3

```


