---
title: "607 Assignment 3"
author: "Katherine Evers"
date: "2/9/2019"
output: html_document
---

3. Copy the introductory example. The vector name stores the extracted names.  

   R> name
[1] "Moe Szyslak" "Burns, C. Montgomery" "Rev. Timothy Lovejoy"
[4] "Ned Flanders" "Simpson, Homer" "Dr. Julius Hibbert"

```{r}
raw.data <- "555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"

library(stringr)

name <-  unlist(str_extract_all(raw.data, "[[:alpha:]., ]{2,}"))
name

swapNames <- str_replace_all(name, "(\\w+),\\s(\\w+)", "\\2 \\1")
swapNames 

```
```{r}
firstName1 <- unlist(str_extract_all(name, "[[:alpha:]]{2,} "))
firstName1 
# "Moe "     "Timothy " "Ned "     "Julius " 

firstName2 <- unlist(str_extract_all(name, "[.,] [[A-z]]{2,}$"))
firstName2
# ". Montgomery" ", Homer" 

firstName2 <- unlist(str_extract_all(firstName2, "[^[:punct:]]"))
firstName2
" " "M" "o" "n" "t" "g" "o" "m" "e" "r" "y" " " "H" "o" "m" "e" "r"

firstName <- unlist(str_extract_all(name, "[[:alpha:]]{2,}|[.,] [[A-z]]{2,}$ "))
firstName 
#[1] "Moe"        "Szyslak"    "Burns"      "Montgomery" "Rev"        "Timothy"    "Lovejoy"    "Ned"       
 #[9] "Flanders"   "Simpson"    "Homer"      "Dr"         "Julius"     "Hibbert"   

firstNames <- c(firstName1, firstName2)
firstNames
#"Moe "         "Timothy "     "Ned "         "Julius "      ". Montgomery" ", Homer"   

firstNames <- unlist(str_extract_all(firstNames, "^.?"))
firstNames

firstName3 = gsub('([[:upper:]])', ' \\1', firstName2)
firstName3
#"MontgomeryHomer"

firstName2 <- str_c(firstName3)
firstName2
" Montgomery Homer"

firstName25 <- unlist(str_extract_all(firstName2, "[^[:punct:]]"))
firstName25

firstName2 <- unlist(strsplit(firstName2, "\\ "))
firstName2

firstNames <- c(firstName1, firstName2)
firstNames

firstNames2 = gsub('([[:upper:]])', ' \\1', firstNames)
firstNames2
```
firstName <- unlist(str_extract_all(name, "[.,] [[A-z]]{2,}$|[[A-z]]{2,} "))
firstName

firstName <- unlist(str_extract_all(name, "[,? [A-z]]{2,}$"))
firstName
#"Moe Szyslak"      " Montgomery"      " Timothy Lovejoy" "Ned Flanders"     "Simpson, Homer"   " Julius Hibbert"


firstName <- unlist(str_extract_all(name, ",+ [[:alpha:]]{2,}"))
firstName 
#", Homer"

firstName <- unlist(str_extract_all(name, " [.+[:alpha:]]{2,}$"))
firstName 
# " Szyslak"    " Montgomery" " Lovejoy"    " Flanders"   ", Homer"     " Hibbert" 


    (a) Use the tools of this chapter to rearrange the vector so that all elements conform to the standard first_name last_name.

    (b) Construct a logical vector indicating whether a character has a title (i.e., Rev. and Dr.).
    
    (c) Construct a logical vector indicating whether a character has a second name.

4. Describe the types of strings that conform to the following regular expressions and construct an example that is matched by the regular expression.

    (a) [0-9]+\\$
        This expression returns a string of 1 or more numbers followed by a $.
        
```{r}
example1 <- "35iu68903$64678$t8bhj$246"
str_extract_all(example1, "[0-9]+\\$" )
```
        
    
    (b) \\b[a-z]{1,4}\\b
        This expression returns a string of 1-4 lowercase letters
```{r}
example2 <- c("abc", "de", "f", "ghij", "kl123")
str_extract_all(example2, "\\b[a-z]{1,4}\\b")
```
        
    
    
    (c) .*?\\.txt$
        This expression returns 
    
    (d) \\d{2}/\\d{2}/\\d{4}
        This string returns a date format: any 2 digits, forward slash, any 2 digits, forward slash, any 4 digits
        
```{r}
example3 <- c("02/11/2019", "2/11/19", "04/02/2018", "1789/12", "12387689")
str_extract_all(example3, "\\d{2}/\\d{2}/\\d{4}")
```
        
    
    (e) <(.+?)>.+?</\\1>
        This expression returns 

9. The following code hides a secret message. Crack it with R and regular expressions. Hint: Some of the characters are more revealing than others! The code snippet is also
available in the materials at www.r-datacollection.com.

    clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr
    
```{r}
message <- "clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr"

message <- unlist(str_extract_all(message, "[^[:digit:]]"))
message
```

